Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation

### 2011-02-14 Multiresolution_framework/ltx/manuscript.tex
edits to MRA section

 % TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
%    \documentclass[journal,a4paper]{IEEEtran}
%     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
%         \topmargin       -6.0mm
%          \oddsidemargin      0mm
%          \evensidemargin     0mm
%          \textheight     223.5mm
%         \textwidth      170.0mm

@@

Assuming $z_t(.)$ and $k(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the integral (\ref{eq:ConvolutionIntegral}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$. For the one-dimensional kernel this is given by,

@@

 k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(s-r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(s-r\right) 

@@

In this expansion, $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$ and $ \beta_{j,l}$ represent the detail coefficients at different scales $j$, with $\phi_{j,l}\left(s\right)=2^{\frac{j}{2}}\phi\left(2^js-l\right) $ and $\psi_{j,l}\left(s\right)=2^{\frac{j}{2}}\psi\left(2^js-l\right)$. Integers $j$ and $l$ are called scale and translation parameters accordingly. The one-dimensional field can similarly be decomposed as

@@

 z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(s\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(s\right)

@@

 \phi_{j,\mathbf{l}}\left(s_1,s_2\right)=\phi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right)

@@

and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{s}\right)$ where $n=1,2,3$ as

@@

 \psi_{j,\mathbf{l}}^{(1)}\left(s_1,s_2\right)=\phi_{j,l_1}\left(s_1\right)\psi_{j,l_2}\left(s_2\right)

@@

 \psi_{j,\mathbf{l}}^{(2)}\left(s_1,s_2\right)=\psi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right)

@@

 \psi_{j,\mathbf{l}}^{(3)}\left(s_1,s_2\right)=\psi_{j,l_1}\left(s_1\right)\psi_{j,l_2}\left(s_2\right)

@@

  \phi_{j,\mathbf{l}}\left(s_1,s_2, \cdots s_d\right)&=&\phi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right) \cdots \phi_{j,l_d}\left(s_d\right) \label{eq:d-dimensionalscalingfunction}\\

@@

and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{s}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case. Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by

@@

 k\left(\mathbf{s}-\mathbf{r}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{s}-\mathbf{r}\right) \nonumber \\
&+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{s}-\mathbf{r}\right) 

@@

z_t\left(\mathbf{s}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{s}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{s}\right)

@@

 k\left(\mathbf{s}-\mathbf{r}\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{s}-\mathbf{r}\right)

@@

 z_t\left(\mathbf{s}\right)\approx\boldsymbol\mu\left(\mathbf{s}\right)^\top\mathbf{x}_t

@@

 \boldsymbol\lambda^\top(\mathbf s-\mathbf r)&=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf s-\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf s-\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf s-\mathbf r) \right. \nonumber \\

@@

 \boldsymbol\mu^\top(\mathbf s)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf s) \quad \boldsymbol\psi_{j_0}^\top(\mathbf s) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf s) \cdots \boldsymbol\psi_{j}^\top(\mathbf s) \right] 

>>>>

 % TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
%    \documentclass[journal,a4paper]{IEEEtran}
     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
%     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
%         \topmargin       -6.0mm
%          \oddsidemargin      0mm
%          \evensidemargin     0mm
%          \textheight     223.5mm
%         \textwidth      170.0mm

@@

Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$. For the one-dimensional kernel this is given by,

@@

 w\left(r-r'\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(r-r'\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(r-r'\right) 

@@

In this expansion, $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$ and $ \beta_{j,l}$ represent the detail coefficients at different scales $j$, with $\phi_{j,l}\left(r\right)=2^{\frac{j}{2}}\phi\left(2^jr-l\right) $ and $\psi_{j,l}\left(r\right)=2^{\frac{j}{2}}\psi\left(2^jr-l\right)$. Integers $j$ and $l$ are called scale and translation parameters accordingly. The one-dimensional field can similarly be decomposed as

@@

 v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(r\right)

@@

 \phi_{j,\mathbf{l}}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)

@@

and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right)$ where $n=1,2,3$ as

@@

 \psi_{j,\mathbf{l}}^{(1)}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)

@@

 \psi_{j,\mathbf{l}}^{(2)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)

@@

 \psi_{j,\mathbf{l}}^{(3)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)

@@

  \phi_{j,\mathbf{l}}\left(r_1,r_2, \cdots r_d\right)&=&\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right) \cdots \phi_{j,l_d}\left(r_d\right) \label{eq:d-dimensionalscalingfunction}\\

@@

and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case. Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by

@@

 k\left(\mathbf{r}-\mathbf{r'}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{r}-\mathbf{r'}\right) \nonumber \\
&+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}-\mathbf{r'}\right) 

@@

z_t\left(\mathbf{r}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{r}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}\right)

@@

 w\left(\mathbf{r}-\mathbf{r'}\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)

@@

 v_t\left(\mathbf{r}\right)\approx\boldsymbol\mu\left(\mathbf{r}\right)^\top\mathbf{x}_t

@@

 \boldsymbol\lambda^\top(\mathbf r-\mathbf r')&=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right. \nonumber \\

@@

 \boldsymbol\mu^\top(\mathbf r)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r) \cdots \boldsymbol\psi_{j}^\top(\mathbf r) \right] 
